ARuko and Editour: \\ A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex
finish second draft

% stuff for LaTeX to know
\bibliography{references}
\graphicspath{ {./images/} } % put images in here
\title{%
	\huge ARuko and Editour: \\
	\Large A Platform for Augmented Reality Tour Guide Apps}
\author{William~Campbell, Cole~Granof, and Joseph~Petitti}
\date{October 11, 2019}

@@

% title page
\begin{center}
	{\huge ARuko and Editour: \\
		\Large A Platform for Augmented Reality Tour Guide Apps
	}

@@

ARuko went through multiple iterations of user testing and bug testing at
Kinkaku-ji. Sections~\ref{sec:initialFieldTesting} and
\ref{sec:finalFieldTesting} go into detail about our two days of field testing
on-site. From these tests, we were able to refine the user experience, and
identify important features to add to the app. Much of the app's functionality
was decided by our project sponsor, who plans to monetize the app. We also
worked with an IQP team, who had been tasked with exploring funding options and
creating promotional content.

@@

In most app development scenarios, to test the app on actual hardware, it must
be compiled using either Xcode or Android Studio depending on your platform.
Once you have built the app, your device needs to install the app. This process
can be very time consuming, especially when needing to run frequent tests on
the target platform.

@@

As an alternative to emulation or compiling a native binary, ViroReact offers a
convenient ``test bed'' for rapidly testing your ViroReact app on native
hardware without the need for an emulator. This allowed us to launch a working
AR app on our devices much more easily than any of the other frameworks or
engines we explored. Unfortunately, the test bed app was somewhat unreliable
based on our experience; the test bed would frequently crash or would not be
able to download the files from the server. The most reliable way to test our
app was to compile a binary and manually install it onto our devices, which
completely defeated the purpose of the test bed app.

@@

For testing and development purposes the Editour backend was originally hosted
on Joseph Petitti's personal server. This was a CentOS virtual machine running
on an old Dell rack server in Worcester, Massachusetts. We wrote a custom
systemd service to run the Editour as a daemon and keep its log files organized.
The Node.js backend was served by an Nginx reverse proxy running on the same
virtual machine.

While this worked well enough for testing, it was not a permanent solution. We
asked Atticus to provide a more powerful---and geographically closer---hosting
solution for running the Editour in the future. He obtained a domain name and a
shared hosting environment on a Red Hat Enterprise Linux (RHEL) server for us to
use on September 23\textsuperscript{rd}. Unfortunately, this shared hosting
environment was designed for running simple PHP applications like WordPress, so
it took a bit of work to coerce it into running a Node.js application.

@@

Furthermore, we foresee Editour being a useful tool outside of the app we
designed for Kyoto~VR. The design of the Editour is agnostic about how the media
will be used. For an app like izi.TRAVEL, the images are displayed when the
associated audio tour is playing.

@@

% TODO let's triple check the name in Japanese even makes sense
ARuko, named after the Japanese word ``\begin{CJK}{UTF8}{min}歩こ\end{CJK}''
(\textit{aruko}), meaning ``let's walk,'' is the app we created to guide users
through an AR-enhanced tour. The app was built with Unity, which enabled to us
to use a single codebase for the iOS and Android versions of the apps.

@@

The core user experience of ARuko is the walking tour. By walking the given
route, the user enters and exits specific geographic regions that invoke
changes in the app, such as playing audio and displaying different images.
Originally, we planned to mark regions by singular points, and trigger that
region if the user was within a certain radius of that point.
Implementation-wise, this would have been much simpler, but obviously limits
possible tour designs. Consequently, we decided at an early stage to
accommodate regions with arbitrary shape and size.  In the implementation, we
provided support for both ``GPS Bubbles'' and ``GPS Polygons.'' In the end
however, Editour made it trivial to use the more versatile ``GPS Polygons,'' so
we eventually dropped support for regions triggered by distance.

@@

% TODO include photos of the google translation app including our own app
ARuko uses augmented reality to translate text at the site as well. While AR
translation apps exist, the experience can be frustrating, and produce poor
results. Google's text recognition and machine-learning powered translation
technology is certainly impressive. At the same time, the translation service
works better in ``scan'' mode instead of ``instant'' mode. In ``instant'' mode,
the app attempts to translate text as quickly as possible, superimposing the
translated text onto the real world using the camera. In ``scan'' mode, the user
first takes a photo. Then, the user is prompted to highlight where text appears
in the photo. After the translation is complete, the translated text appears in
a separate UI element instead superimposed onto the photo. In most cases, it is
more convenient and readable to have the translation appear in a separate
scrollable text box. This motivated the current design of the ``info buttons''
in ARuko. Instead of placing text directly onto signage, we place a blue button
with a stylized `i' in the center. By tapping on this button, a separate UI
element will appear containing the translated text. Since this button is cast
into the world using the AR camera, the button appears to be placed directly
onto the content in the real world.

@@

Near the entrance of Kinkaku-ji before the ticket gate, there is a large
illustrated map. Much like the signage, there is no language on the map other
than Japanese. Using the AR camera within the app, information can be projected
onto the map. Figure~\ref{fig:arMapFeature} shows the blue highlighted path of
the walking tour, including a few translated labels.

\begin{figure}[h] \centering
    \includegraphics[width=0.4\textwidth]{ar-map-feature.png}
    \caption{Map overlay displaying the path and translated labels}
    \label{fig:arMapFeature}
\end{figure}

@@

Tickets to enter Kinkaku-ji are long sheets of printed paper with calligraphy.
The tickets are large and visually appealing; they are souvenirs unto themselves
that one might feel inclined to keep around. Over the course of our three month
stay we visited Kinkaku-ji multiple times. For each visit, we received identical
tickets. Seemingly, the design on the tickets do not change on a regular basis,
if at all. Figure~\ref{fig:kinkakujiTicket} shows a ticket we kept from one of
our visits to Kinkaku-ji.

@@

Because the tickets are unlikely to change frequently, this enables us to
provide the user with a ``virtual souvenir'' using the AR camera. This is the
only AR feature that is not tied directly to an image target that can only be
accessed at Kinkaku-ji. While the image gallery and segments of the audio tour
can be accessed at any time using the ``Chapter Select'' menu, most of the AR
features can only be experienced during the walking tour, pointing the camera at
objects physically located at the site. Augmenting the ticket with 3D content
allows visitors to take something home, giving them a reason to launch the app
later.

We found a free untextured model of the Golden Pavilion to use for this
feature. Using Unity's built-in capability to design materials, we created
a shiny golden material and applied it to the model (see
Figure~\ref{fig:souvenir}.

@@

As ideas changed and ARuko became what it is today, the user interface (UI) also
changed greatly from its early conception to the final version. Still, the early
UI was a valuable learning experience, providing us with skills that were useful
when building the final version.

The early UI was very much a product of ARuko's development; many of its
elements were created on the fly as new features were added. As more features
were added, it became clear that the UI could not consist simply of buttons and
other basic features provided by Unity. We would need to learn more about how to
create more interesting and useful UI elements to accommodate for our new
functionality.

@@

Pictured in Figure~\ref{fig:oldUI} is our early UI. It was a very minimal UI,
but still covered all of the uses for our app at the time. The top of the screen
had two dropdown menus. The one on the left (which is open shown open in
Figure~\ref{fig:oldUI}) shows AR image targets in the area that users could
look for and scan. The right dropdown would be dynamically populated in each
region with buttons bearing different images. These images were ones that
Atticus wanted to be viewable in AR using ground plane detection. When tapped,
each button would create a 3D Cube, with the given image on each face, and place
it on the ground where the user was pointing. Figure~\ref{fig:floatingCube}
shows this feature in action.

@@

Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
target capabilities for scanning objects outside of the expected use case, such
as 3D landscapes or the side of a building. We had serious doubts about how
well this would work, and our suspicions were confirmed after some field
testing. This was the reasoning behind focusing on ground-plane detection
instead of image targets; ground-plane detection can be used anywhere, and is
much more reliable than treating 3D objects as 2D image targets.

Learning to create these dropdown menus proved to be a very important lesson
later on, since we would put that exact knowledge to use multiple times in the
final UI. We were able to create the dynamically populated dropdown menus by
creating an empty vertical layout group. Then, a script would create buttons for
each image to display, and assign those images as children of the layout group.
Then, to get the smooth open/close animation, we ``lerp'' (linearly interpolate)
the menu to the corresponding position each frame until it is fully open or
closed. In between these two dropdown menus is a panel that would display the
name for the region the user is in at the time. The empty space in the middle of
the screen is where the AR camera display would be shown. In this
implementation, the AR functionality was the focus of the app, so it made sense
to display the AR camera feed at all times. Lastly, on the bottom is the audio
slider for the audio file played in each region. We learned about how audio
sliders work in Unity with this feature, and would expand on that knowledge for
the final version of the app in order to optimize the slider's functionality.

Although most elements of the initial UI did not survive into the final product,
it was still quite valuable as a learning tool. While crafting this prototype we
discovered many of the intricacies of UI design in Unity. For example, all UI
elements must be attached to a Unity canvas element, which covers the entire
phone screen. Elements should be anchored to edges or corners of this canvas so
that they stay in a constant location on different-size screens.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{editour-additions.png}
	\caption{Additions to the Editour to accommodate the new design}
	\label{fig:editourAdditions}
\end{figure}

@@

The last major UI implementation obstacle we had to overcome was a way to keep
audio playing with the phone in your pocket. Atticus insisted that this sort of
feature was required so that users could listen to the audio tour without using %maybe include an image of pocket mode here
any of the other functionality the app provides, like the image gallery in each
region or the AR features. Despite how common it is for apps to play audio in
the background or while the phone is locked, Unity does not provide a way to
accomplish this. Our workaround was to create a ``pocket mode'' that prevents UI
elements from accidentally being triggered. The user exits pocket mode with a
deliberate swipe to the right. If the slider is released partway through the
action, the slider springs back to the beginning. We were ultimately able to
replicate Atticus's Adobe XD file almost perfectly.

@@

Both pieces of our project---Editour and ARuko---are designed to be used by
people who are not programmers. Editour will be used by Atticus in the future to
design more tours, and ARuko will be used by the general public. Because of
this, we needed to do extensive testing to ensure not only that the products
work as intended without bugs, but also that they would be pleasant and easy to
use for their intended users.

% TODO remove this
\nocite{harvey2002} % don't remove this

@@

We suspect that Editour might have a life outside of this particular use case
depending on how it is developed later on. This is why Editour is perhaps more
polished than your typical tool purely for internal use.

@@

Because it was not feasible to travel to Kinkaku-ji every time we needed to test
the GPS functionality of the app, we used Editour to design an example tour
around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed us to
catch various bugs before we created a finalized prototype for field-testing at
Kinkaku-ji. The tour represented in Figure~\ref{fig:ritsuTour} is what we used
for testing the app. The ``C-Shaped Region'' helped us test concave regions.
This uniquely shaped region also prompted us to think about what UI behavior
made the most sense if a user were to walk into a region, walk out and then in
again. We decided that it was awkward if the audio restarted upon re-entering a
region, since the audio would still be playing once a user left the region. As
we began to implement more complex UI that changed based on GPS position in
various ways, directly taking the tour by walking around was an invaluable way
to test. Section~\ref{sec:adobeXdDesign} details how the UI grew in complexity
in the late stages of the project. Having a way to regularly run field tests was
integral to polishing the app in time before we revisited Kinkaku-ji.  Because
the Editour was flexible enough to easily swap out media and add regions to the
tour, the Editour proved itself to be as helpful for testing as it was for
crafting the final tour that could be taken at Kinkaku-ji.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{four-i-buttons.png}
	\caption{The result of increasing the size of the info buttons and increasing
    the maximum image target count to four}
	\label{fig:fourIButtons}
\end{figure}

@@

We spent the second and third week of the project creating demos to explore the
possibility of a 3D spatialized audio tour. We found that this would be very
difficult to do without the use of the camera. All of the technology for mobile
AR we explored in Section~\ref{sec:platforms} depended heavily on the camera. If
we were to build a 3D spatialized audio tour that ran entirely without use of
the camera, we would not be able to take advantage of any of the useful features
of the AR libraries we explored. Furthermore, Unity would be relegated to the
simple role of exporting our app to multiple devices; we would not have any need
to take advantage of its 3D capabilities.

Thusly, we decided to see what was possible using the camera instead. We were
able to get sound sources to fade in and out based on the distance to an image
target. Naturally, if the image target were to go out of view of the camera,
Vuforia stopped trying to estimate the camera's distance to the last known
location of the image target. In order to make this work in the way Atticus
imagined, we would need a way to shift to our own method of estimating distance
to the sound source once the image target had been lost. While this might have
been possible, it was difficult to estimate the amount of effort this would
take, since we would essentially be implementing a feature seemingly not
supported by current AR libraries.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.7\textwidth]{exhibition-scan.png}
    \caption{A screenshot of the 3D scan of `Portraits of Thought,' accessible
    from the web}
	\label{fig:exhibitionScan}
\end{figure}

\subsection{Alterniative Uses for AR in ARuko}
\label{sec:alternativeARukoAR}

Even once the idea for ARuko was settled on audio tour functionality with 
additional AR components, what exactly those AR components would do was still
undecided until more details about the project crystallized. Atticus knew he 
wanted to use AR on the tour, but was not sure what to do with it. At first, we
made recommendations to him based on the capabilities of Vuforia that we found 
in our research. We knew it was good at image recognition and ground plane 
recognition, so we suggested that maybe displaying some sorts of 3D models in 
certain locations using either of these features might be an interesting way to
expand on the tour. With these recommendations in mind, Atticus expressed 
interest in the capability of using building facades as image targets. The 
intention then would be to tie content related to a specific location within 
Kinkaku-ji to that physical location, and use images of the location as 
targets. As previously explained, this ultimately did not work out due to the 
limitations of image recognition with Vuforia.

After being initially deterred from image recognition, we thought that ground
and mid-air plane recognition might the best way to implement AR in the app. 
It did not have to rely on images that meet Vuforia's criteria, and since it 
could be triggered anywhere, it seemed like a good fit for an app focusing on
walking around a site. Atticus explained that he primarily wanted to use AR to
display art related to the site. With this in mind, we focused our efforts with
ground and mid-air plane AR on ways to display 2D images. What we ended up 
creating first was a feature that allowed users to view certain images in AR, 
using ground plane detection, based on what region you were in. When users 
entered a region of the tour, the image menu would be dynamically populated 
with buttons that, when tapped, would create a Plane primitive in Unity with 
the given image displayed on it and place it on the ground plane.

We encountered a few notable problems with this though. One problem was that 
the Plane we made was always the same size and dimensions, and would cause 
images to stretch to fit the plane. Further testing to change the size of the
plane with each picture proved difficult. Additionally, using a Plane primitive
had problematic effects on the way the object was lit in the Unity scene, as 
well as how it appeared when not viewed head-on. If viewed from an angle, the 
picture could become very dark and difficult to see. If viewed from behind,
back-face culling would take effect and the plane would become completely 
invisible. Because of these issues, we decided to place the images on a 3D Cube
primitive instead. But after showing this feature to Atticus during early 
testing at Kinkaku-ji, he decided that he wanted to move away from displaying 
images in AR. Looking back, the feature may have worked better with mid-air 
plane recognition so that the user could place the image directly in front of 
them.

In addition to the previously mentioned use cases for AR in ARuko, Atticus also
expressed interest in using AR to trigger video content. He was particularly
interested in 3D videos triggerable through AR. As the scope of the project 
grew, and time ran short, the task of including 3D videos triggered by AR 
seemed more and more complicated, causing that idea to be phased out of the
final project. Additionally, we never received any assets from Atticus to use
for this feature, thus preventing us from spending time developing it.

@@

Partway through our project, Atticus Sims let us know that he was looking to
monetize the app we were developing for him. He also informed us that the IQP
team would be looking for funding options in order to ``bootstrap'' the project.
One monetization method he proposed was potentially marketing the app to hotels,
allowing hotels to sell tours for download through in-app purchases.

In order to get an app approved for the App Store or the Google Play store,
there is sometimes a lengthy approval process. This might have been possible if
our project had been more prescriptive from the start.

We did perform some preliminary research about the monetization models Atticus
proposed and brought forth some potential roadblocks regarding each one. We let
Atticus know that we had logistical concerns about circumventing Apple's or
Google's in-app purchases by locking content behind a different payment process.
Additionally, we informed Atticus that he would have to purchase a commercial
Vuforia license in order to deploy the app onto any
storefront~\autocite{vuforialicense2018}, which Atticus was not willing to do at
the time. The free version of Vuforia comes branded with a watermark in the
bottom left corner.\footnote{The final design of our app incidentally covers up
the watermark with our own UI elements. This does not change the fact that we
would not be able to deploy the app without a proper commercial license for
Vuforia.}

Our concerns about focusing on monetization for Kyoto~VR were twofold. Firstly,
we were worried that this kind of work strayed too far away from the academic
intent of the project---the intent being to explore various ways in which AR and
geolocation could be used in tandem to create an improved experience for
tourists. For our purposes, the app was meant to demonstrate our discoveries in
the form of a polished prototype. While we feel as though we achieved this goal,
we made certain compromises in the way of experimentation in order to leave
Kyoto~VR with a potentially marketable product. We made it clear to Atticus that
deploying our app on the Google Play Store or App Store would not be within the
scope of our academic project as per our advisers' advice.

@@

Our team is satisfied with the final result of this project, as we feel we have
built a working platform that Kyoto~VR will easily be able to build off of in
the future. This section contains our final thoughts on the project and future
work that could be done on it.

@@

On a similar note, the requirements and scope of the project changed greatly
from week to week, and sometimes even within one day. We spent a significant
amount of time exploring concepts and features that were completely unrelated to
the final product. We also did not receive official specifications, such as the
design of the GUI Atticus wanted for the app, until very late in the development
process.

@@

\subsubsection{What Went Well}
\label{sec:whatWentWell}

Despite these issues, in the end we were able to create a useful working
prototype. The Editour is fully featured with everything needed to build an
audio tour anywhere in the world. ARuko allows users to experience useful
AR-enhanced tours in a pleasant and intuitive way. Together they provide a
complete platform for building augmented reality tour guide apps.

>>>>

% stuff for LaTeX to know
\bibliography{references}
\graphicspath{ {./images/} } % put images in here
\title{%
	ARuko and Editour: \\
	A Platform for Augmented Reality Tour Guide Apps}
\author{William~Campbell, Cole~Granof, and Joseph~Petitti}
\date{October 11, 2019}

@@

% title page
\begin{center}
	{\huge ARuko and Editour: \\
		\vspace{.5\baselineskip}
		\Large A Platform for Augmented Reality Tour Guide Apps
	}

@@

ARuko went through multiple iterations of user testing and bug testing at
Kinkaku-ji. Sections~\ref{sec:initialFieldTesting} and
\ref{sec:finalFieldTesting} go into detail about our two days of field testing
on-site. From these tests, we were able to refine the user experience, and
identify important features to add to the app. Much of the app's functionality
was decided by our project sponsor, who plans to monetize the app. We also
worked with an Interactive Qualifying Project (IQP) team, who had been tasked
with exploring funding options and creating promotional content.

@@

In most app development scenarios, to test the app on actual hardware, it must
be compiled using either Xcode or Android Studio depending on the target
platform. Once you have built the app, it must be installed on the device. This
process can be very time consuming, especially when needing to run frequent
tests on the target platform.

@@

As an alternative to emulation or compiling a native binary, ViroReact offers a
convenient ``test bed'' for rapidly testing ViroReact apps on native
hardware without the need for an emulator. This allowed us to launch a working
AR app on our devices much more easily than any of the other frameworks or
engines we explored. Unfortunately, the test bed app was somewhat unreliable
based on our experience; the test bed would frequently crash or would not be
able to download the files from the server. The most reliable way to test our
app was to compile a binary and manually install it onto our devices, which
completely defeated the purpose of the test bed app.

@@

For testing and development purposes the Editour backend was originally hosted
on Joseph Petitti's personal server. This was a CentOS virtual machine running
on an old Dell rack server in Worcester, Massachusetts. We wrote a custom
systemd service to run Editour as a daemon and keep its log files organized. The
Node.js backend was served by an Nginx reverse proxy running on the same virtual
machine.

While this worked well enough for testing, it was not a permanent solution. We
asked Atticus to provide a more powerful---and geographically closer---hosting
solution for running Editour in the future. He obtained a domain name and a
shared hosting environment on a Red Hat Enterprise Linux (RHEL) server for us to
use on September 23\textsuperscript{rd}. Unfortunately, this shared hosting
environment was designed for running simple PHP applications like WordPress, so
it took a bit of work to coerce it into running a Node.js application.

@@

Furthermore, we foresee Editour being a useful tool outside of the app we
designed for Kyoto~VR. The design of Editour is agnostic about how the media
will be used. For an app like izi.TRAVEL, the images are displayed when the
associated audio tour is playing.

@@

% TODO let's triple check the name in Japanese even makes sense
ARuko, named after the Japanese word ``\begin{CJK}{UTF8}{min}歩こ\end{CJK}''
(\textit{aruko}), meaning ``let's walk,'' is the app we created to guide users
through an AR-enhanced tour. The app was built with Unity, which enabled to us
to use a single codebase for the iOS and Android versions of the app.

@@

The core user experience of ARuko is the walking tour. By walking the given
route, the user enters and exits specific geographic regions that invoke
changes in the app, such as playing audio and displaying different images.
Originally, we planned to mark regions by singular points, and trigger that
region if the user was within a certain radius of that point.
Implementation-wise, this would have been much simpler, but obviously limits
possible tour designs. Consequently, we decided at an early stage to
accommodate regions with arbitrary shape and size.  In the implementation, we
provided support for both ``GPS Bubbles'' and ``GPS Polygons.'' In the end
however, Editour made it trivial to use the more versatile ``GPS Polygons,'' so
we eventually dropped support for regions triggered by distance.
% TODO add a picture that shows how having only circular regions limits possible
% tour designs

@@

ARuko uses augmented reality to translate text at the site of the tour as well.
While AR translation apps exist, the experience can be frustrating, and produce
poor results. Google~Translate's text recognition and machine-learning powered
translation technology is certainly impressive. At the same time, the
translation service works better in ``scan'' mode instead of ``instant'' mode.
In ``instant'' mode, the app attempts to translate text as quickly as possible,
superimposing the translated text onto the real world using the camera. In
``scan'' mode, the user first takes a photo. Then, the user is prompted to
highlight where text appears in the photo. After the translation is complete,
the translated text appears in a separate UI element. In most cases, it is more
convenient and readable to have the translation appear in a separate scrollable
text box. This motivated the current design of the ``info buttons'' in ARuko.
Instead of placing text directly onto signage, we place a blue button with a
stylized ``\textit{i}'' in the center. By tapping on this button, a separate UI
element will appear containing the translated text. Since this button is cast
into the world using the AR camera, the button appears to be placed directly
on top of the content.
% TODO images for this section

@@

Near the entrance of Kinkaku-ji before the ticket gate, there is a large
illustrated map. Much like the signage, there is no language on the map other
than Japanese. Using the AR camera within the app, information can be projected
onto the map. Figure~\ref{fig:arMapFeature} shows the blue highlighted path of
the walking tour, including a few translated labels. The blue path and English
text are not part of the physical map. These are superimposed on the image by
ARuko.

\begin{figure}[p]
	\centering
    \includegraphics[width=0.8\textwidth]{ar-map-feature.png}
    \caption{Map overlay displaying the path and translated labels}
    \label{fig:arMapFeature}
\end{figure}

@@

Tickets to enter Kinkaku-ji are long sheets of paper printed with calligraphy.
The tickets are large and visually appealing; they are souvenirs unto themselves
that one might feel inclined to keep around. Over the course of our three month
stay we visited Kinkaku-ji thrice. For each visit, we received identical
tickets. Seemingly, the design on the tickets do not change on a regular basis,
if at all. Figure~\ref{fig:kinkakujiTicket} shows a ticket we kept from one of
our visits to Kinkaku-ji.

@@

Because the tickets are unlikely to change frequently, we are able to provide
the user with a ``virtual souvenir'' using the AR camera. This is the only AR
feature that is not tied directly to an image target that can only be accessed
at Kinkaku-ji. While the image gallery and segments of the audio tour can be
accessed at any time using the ``Chapter Select'' menu, most of the AR features
can only be experienced during the walking tour, pointing the camera at objects
physically located at the site. Augmenting the ticket with 3D content allows
visitors to take something home, giving them a reason to launch the app later.

We found a free untextured model of the Golden Pavilion to use for this feature
on Thingiverse, a site for sharing user-created 3D
models~\autocite{baichtal2008}. Using Unity's built-in capability to design
materials, we created a shiny golden material and applied it to the model (see
Figure~\ref{fig:souvenir}).

@@

As ideas changed and ARuko became what it is today, the user interface (UI) also
changed greatly from its early conception to the final version. Still, the early
UI was a valuable learning experience, providing us with skills that were useful
when building the finished product.

The early UI was purely functional with no bells or whistles; many of its
elements were created on the fly as new features were added. As the app grew,
it became clear that the UI could not consist simply of buttons and other basic
features provided by Unity.

@@

Pictured in Figure~\ref{fig:oldUI} is our early UI. It was very minimal, but
still covered all of the uses for our app at the time. The top of the screen had
two drop-down menus. The one on the left (which is shown open in
Figure~\ref{fig:oldUI}) shows AR image targets users could look for and scan.
The right drop-down would be dynamically populated in each region with buttons
bearing different images. These images were ones that Atticus wanted to be
viewable in AR using ground plane detection. When tapped, each button would
create a cube, with the given image on each face, and place it on the ground
where the user was pointing. Figure~\ref{fig:floatingCube} shows this feature in
action.

@@

Atticus initially wanted us to explore the efficacy of using Vuforia's 2D image
target capabilities for scanning objects outside of the supported use case, such
as 3D landscapes or the side of a building. We had serious doubts about how
well this would work, and our suspicions were confirmed after some field
testing. This was the reasoning behind focusing on ground-plane detection
instead of image targets; ground-plane detection can be used anywhere, and is
much more reliable than treating 3D objects as 2D image targets.

Learning to create these drop-down menus proved to be a very important lesson
later on, since we would put that exact knowledge to use multiple times in the
final UI. We were able to create the dynamically populated drop-down menus by
creating an empty vertical layout group. Then, a script would create buttons for
each image to display, and assign those images as children of the layout group.
To get the smooth open/close animation, we ``lerp'' (linearly interpolate)
the menu to the corresponding position each frame until it is fully opened or
closed. In between these two drop-down menus is a panel that would display the
name for the region the user is in at the time. The empty space in the middle of
the screen is where the AR camera display would be shown. In this
implementation, the AR functionality was the focus of the app, so it made sense
to display the AR camera feed at all times. Lastly, on the bottom is a slider
that controls the playback position of the audio file played in each region. We
learned about how audio sliders work in Unity with this feature, and would
expand on that knowledge for the final version of the app in order to optimize
the slider's functionality.

Although most elements of the initial UI did not survive into the final product,
this original phase was still quite valuable as a learning tool. While crafting
this prototype we discovered many of the intricacies of UI design in Unity. For
example, all UI elements must be attached to a Unity canvas element, which
covers the entire phone screen. Elements should be anchored to edges or corners
of this canvas so that they stay in a constant location on screens of different
sizes.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{editour-additions.png}
	\caption{Additions to Editour to accommodate the new design}
	\label{fig:editourAdditions}
\end{figure}

@@

The last major UI implementation obstacle we had to overcome was a way to keep
audio playing with the phone in a pocket. Atticus desired this sort of feature
so that users could listen to the audio tour without using any of the other
functionality the app provides, such as the image gallery or the AR
features. Despite how common it is for apps to play audio in the background or
while the phone is locked, Unity does not provide a way to accomplish this. Our
workaround was to create a ``pocket mode'' that prevents UI elements from
accidentally being triggered. The user exits pocket mode with a deliberate swipe
to the right. If the slider is released partway through the action, the slider
springs back to the its original position.
% TODO maybe include an image of pocket mode here

@@

Both pieces of our project---Editour and ARuko---are designed to be used by
people who are not programmers. Editour will be used by Atticus in the future to
design more tours, and ARuko will be used by the general public. Because of
this, we needed to do extensive testing to ensure not only that the products
work as intended without bugs, but also that they are pleasant and easy to use
for their intended users.

\nocite{harvey2002} % don't remove this

@@

We suspect that Editour might have a life outside of this particular use case
depending on how it is developed later on. This is why Editour is perhaps more
polished than typical internal tools.

@@

Because it was not feasible to travel to Kinkaku-ji every time we needed to test
the GPS functionality of the app, we used Editour to design an example tour
around the Ritsumeikan Biwako-Kusatsu campus where we worked. This allowed us to
catch various bugs before we created a finalized prototype for field-testing at
Kinkaku-ji. The tour represented in Figure~\ref{fig:ritsuTour} is what we used
for testing the app. The ``C-Shaped Region'' helped us test concave regions.
This uniquely shaped region also prompted us to think about what UI behavior
made the most sense if a user were to walk into a region, walk out and then in
again. We decided that it was awkward if the audio restarted upon re-entering a
region, since the audio would still be playing once a user left the region. As
we began to implement more complex UI that changed based on GPS position in
various ways, directly taking the tour by walking around was an invaluable way
to test. Section~\ref{sec:adobeXdDesign} details how the UI grew in complexity
in the late stages of the project. Having a way to regularly run field tests was
integral to polishing the app in time before we revisited Kinkaku-ji. Because
Editour was flexible enough to easily swap out media and add regions to the
tour, Editour proved itself to be as helpful for testing as it was for
crafting the final tour that could be taken at Kinkaku-ji.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{four-i-buttons.png}
	\caption{Tracking four image targets at once with improved info buttons.}
	\label{fig:fourIButtons}
\end{figure}

@@

We spent the second and third week of the project creating demonstrations to
explore the possibility of a 3D spatialized audio tour. We found that this would
be very difficult to do without the use of the camera. All of the technology for
mobile AR we explored in Section~\ref{sec:platforms} depended heavily on the
camera. If we were to build a 3D spatialized audio tour that ran entirely
without use of the camera, we would not be able to take advantage of any of the
useful features of the AR libraries we explored. Furthermore, Unity would be
relegated to the simple role of exporting our app to multiple devices; we would
not have any need to take advantage of its 3D capabilities.

Therefore, we decided to see what was possible using the camera instead. We were
able to get sound sources to fade in and out based on the distance to an image
target. Naturally, if the image target were to go out of view of the camera,
Vuforia stopped trying to estimate the camera's distance to the last known
location of the image target. In order to make this work in the way Atticus
imagined, we would need a way to shift to our own method of estimating distance
to the sound source once the image target had been lost. It was difficult to
estimate the amount of effort this would take (and whether it was even
possible), since we would essentially be implementing a feature seemingly not
supported by current AR libraries.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=.7\textwidth]{exhibition-scan.png}
    \caption{A screenshot of the 3D scan of ``Portraits of Thought,'' accessible
    from the web}
	\label{fig:exhibitionScan}
\end{figure}

\subsection{Alternative Uses for AR in ARuko}
\label{sec:alternativeARukoAR}

Even after the core functionality of ARuko was finalized as an audio tour with
additional AR components, the exact nature of those AR components was still
undecided until more details about the project crystallized. Atticus knew he
wanted to use AR on the tour, but was not sure what to do with it. At first, we
made recommendations to him based on the capabilities of Vuforia. We knew that
image recognition and ground plane recognition were two of its strengths, so we
suggested that displaying 3D models in certain locations using either of these
features would be an interesting way to expand on the tour. With these
recommendations in mind, Atticus expressed interest in using building facades as
image targets. The intention then would be to tie content to a physical location
in Kinkaku-ji, and use images of the location as targets. As explained in
Section~\ref{sec:earlyUserInterface}, this ultimately did not work out due to
the limitations of Vuforia's image recognition.

After being initially deterred from image recognition, we thought that ground
and mid-air plane recognition might the best way to implement AR in the app. It
did not have to rely on images that meet Vuforia's criteria, and since it could
be triggered anywhere, it appeared to be a good fit for an app focusing on
walking around a site. Atticus explained that he primarily wanted to use AR to
display art related to the site. With this in mind, we focused our efforts with
ground and mid-air plane AR on ways to display 2D images. What we ended up
creating first was a feature that allowed users to view certain images in AR,
using ground plane detection, based on what region you were in. When users
entered a region of the tour, the image menu would be dynamically populated with
buttons that, when tapped, would create a Plane primitive in Unity with the
given image displayed on it and place it on the ground plane.

We encountered a few notable problems with this. Using a Plane primitive had
deleterious effects on the way the object was lit in the Unity scene, as well as
how it appeared when not viewed head-on. If viewed from an angle, the picture
could become very dark and difficult to see. If viewed from behind, back-face
culling would take effect and the plane would become completely invisible.
Because of these issues, we decided to place the images on a Cube primitive
instead. After showing this feature to Atticus during early testing at
Kinkaku-ji, he decided that he wanted to move away from displaying images in AR.
Looking back, the feature may have worked better with mid-air plane recognition
so that the user could place the image directly in front of them.

In addition to the previously mentioned use cases for AR in ARuko, Atticus also
expressed interest in using AR to trigger video content. He was particularly
interested in triggering 3D videos through AR. As the scope of the project 
grew, and time ran short, the task of including 3D videos triggered by AR 
seemed more and more complicated, causing that idea to be phased out of the
final project. Additionally, we never received any assets from Atticus to use
for this feature, preventing us from spending time developing it.

@@

Partway through our project, Atticus Sims let us know that he was looking to
monetize the app we were developing for him. He also informed us that the IQP
team would be looking for funding options in order to ``bootstrap'' the project.
One monetization method he proposed was marketing the app to hotels,
allowing hotels to sell tours for download through in-app purchases.

Getting an app approved to launch on the App Store or Google Play has many
specific requirements and can be a very lengthy process. This might have been
possible if our project had been more prescriptive from the start and we had
more time.

We did perform some preliminary research about the monetization models Atticus
proposed and brought forth some potential roadblocks regarding each one. We let
Atticus know that we had logistical concerns about circumventing Apple's or
Google's in-app purchases by locking content behind a different payment process
as he suggested. Additionally, we informed Atticus that he would have to
purchase a commercial Vuforia license in order to publish the app on any
storefront~\autocite{vuforialicense2018}, which Atticus was not willing to do at
the time. The free version of Vuforia comes branded with a watermark in the
bottom left corner.\footnote{The final design of our app incidentally covers up
the watermark with our own UI elements. This does not change the fact that we
would not legally be able to deploy the app without a proper commercial license
for Vuforia.}

Our concerns about focusing on monetization for Kyoto~VR were twofold. Firstly,
we were worried that this kind of work strayed too far away from the academic
intent of the project---to explore various ways in which AR and geolocation
could be used in tandem to create an improved experience for tourists. For our
purposes, the app was meant to demonstrate our discoveries in the form of a
polished prototype. While we feel as though we achieved this goal, we restricted
our experimentation in order to leave Kyoto~VR with a potentially marketable
product. We made it clear to Atticus that deploying our app on Google Play
or the App Store would not be within the scope of our academic project as per
our advisers' guidance.

@@

Our team is satisfied with the final result of this project, as we feel we have
built a working platform that Kyoto~VR will easily be able to build off of in
the future. This section contains our final thoughts on the project and future
work that could be done.

@@

On a similar note, the requirements and scope of the project changed greatly
from week to week, and sometimes even within one day. We spent a significant
amount of time exploring concepts and features that were completely unrelated to
the final product. We also did not receive official specifications, such as the
design of the graphical user interface (GUI) Atticus wanted for the app, until
very late in the development process.

@@

\subsection{What Went Well}
\label{sec:whatWentWell}

Despite these issues, in the end we were able to create a useful working
prototype. Editour is fully featured with everything needed to build an
audio tour anywhere in the world. ARuko allows users to experience useful
AR-enhanced tours in a pleasant and intuitive way. Together they provide a
complete platform for building augmented reality tour guide apps.
